Mathematical Gene Network Evolution

### 2017-06-20 attic/model_notes.tex
minor editing

     \section{Notes for May presentation}
       \begin{align*}
         \Sigma(0) := \left\{ \begin{array}{ll}
         \dot{x} &= \left[ \begin{array}{cc} 0 & 1 \\ -1 & 0 \end{array} \right] x + \left[ \begin{array}{c} 1 \\ 1 \end{array}\right] u \\
           y &= \left[ \begin{array}{cc} 1 & 0 \end{array} \right] x
         \end{array} \right.
    \end{align*}

    \begin{align*}
      \Sigma(0) := \left\{ \begin{array}{ll}
      \dot{x}_{1} &= +x_{2} + u \\
      \dot{x}_{2} &= -x_{1} + u \\
      y &= x_{1}
      \end{array} \right.
    \end{align*}

       \begin{align*}
         \Sigma(2) :&= \left\{ \begin{array}{ll}
         \dot{x} &= \left[ \begin{array}{cc} 2 & -1 \\ 5 & -2 \end{array} \right] x + \left[ \begin{array}{c} 1 \\ 1 \end{array}\right] u \\
           y &= \left[ \begin{array}{cc} 1 & 0 \end{array} \right] x
         \end{array} \right. \\ \\
         \Sigma(2) :&= \left\{ \begin{array}{ll}
        \dot{x}_{1} &= 2 x_{1} + - x_{2} + u \\
        \dot{x}_{2} &= 5 x_{1} + -2 x_{2} + u \\
      y &= x_{1}
      \end{array} \right.
    \end{align*}
    \begin{align*}
      \mathcal{L}(\Sigma(\tau)) := H(z, \tau) = C \left(zI - A(\tau) \right)^{-1} B
    \end{align*}

>>>>

     \section{Notes for May presentation}
    \begin{align*}
      \Sigma(0) := \left\{ \begin{array}{ll}
      \dot{x}_{1} &= +x_{2} + u \\
      \dot{x}_{2} &= -x_{1} + u \\
      y &= x_{1}
      \end{array} \right.
    \end{align*}
\newpage
       \begin{align*}
         \Sigma &= \left\{ \begin{array}{ll}
           \dot{\kappa}(t) &= \left[ \begin{array}{cc} 0 & 1 \\ -1 & 0 \end{array} \right] \kappa(t) + \left[ \begin{array}{c} 1 \\ 1 \end{array}\right] u(t) \\
             \phi(t) &= \left[ \begin{array}{cc} 1 & 0 \end{array} \right] \kappa(t)
         \end{array} \right. \\ \\
         \widehat{\Sigma} &= \left\{ \begin{array}{ll}
           \dot{\kappa}(t) &= \left[ \begin{array}{cc} 2 & -1 \\ 5 & -2 \end{array} \right] \kappa(t) + \left[ \begin{array}{c} 1 \\ 1 \end{array}\right] u(t) \\
             \phi(t) &= \left[ \begin{array}{cc} 1 & 0 \end{array} \right] \kappa(t)
         \end{array} \right. \\ \\
         \phi(t) &= \sin(t) + \cos(t)
        % \Sigma(2) :&= \left\{ \begin{array}{ll}
       % \dot{x}_{1} &= 2 x_{1} + - x_{2} + u \\
       % \dot{x}_{2} &= 5 x_{1} + -2 x_{2} + u \\
     % y &= x_{1}
     % \end{array} \right.
    \end{align*}
    \begin{align*}
      \mathcal{L}(\Sigma(\tau)) := H(z, \tau) = C \left(zI - A(\tau) \right)^{-1} B
    \end{align*}
